%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%------------------------------------------------

  \cventry
      {Technical Lead} % Job title
      {Singapore Press Holdings Limited} % Organization
      {Singapore} % Location
      {Jan. 2019 - Present} % Date(s)
      { % Description(s) of tasks/responsibilities
        \begin{cvitems}
          \item {Lead Engineer on the Application Modernization and Cloud Migration of the major publication - Landing Zone, EKS, Jenkins, Spinnaker, EFK, Prometheus, Grafana, Rancher, IaC}
          \item {Review the AWS Landing Zone, Application Architecture and verify against the AWS Well-Architected Framework with AWS Solution Architect.}\newline
          \item {Performance test and tune pod level request limits and RDS parameters - Jmeter}
          \item {Design and architect the Common Mobile Backend System - Go, NodeJs, CloudFront, API Gateway, NLB, ALB, ECS, Elasticsearch, Lambda, Redis}
          \item {Provide review and feedback to colleagues on their systems architecture mainly on AWS}
          \item {RFQ/PoC on container security tools - Prisma Cloud, AquaSec}
          \item {Cache optimization on Verizion CDN.}
          \item {Setting up CDN DR on AWS CloudFront for major domains.}
          \item {IaC for an Elasticsearch cluster and a Drupal System on AWS EC2.}
          \item {Resolving incidents, performing RCA and writing postmortems.}
        \end{cvitems}
      }

%------------------------------------------------    

  \cventry
      {Principal Software Engineer} % Job title
      {Singapore Press Holdings Limited} % Organization
      {Singapore} % Location
      {Jan. 2018 - Jan. 2019} % Date(s)
      { % Description(s) of tasks/responsibilities
        \begin{cvitems}
          \item {DevOps Engineer for all the SPH editorial products and lead developer for Consent Tracking System.}
          \item {Created and managed the Jenkins pipelins.}
          \item {Created and troubleshooted Verizion CDN rules for various publications.}
          \item {Installed and configured Varnish cache servers using Ansible.}
          \item {ELK configuration and Grafana, InfluxDb, Telegraf configurations.}
          \item {Newrelic Infrastructure, APM, Alerts, Synthetic and Insights configuration.}
          \item {Created AWS CI/CD pipeline.}
          \item {mySPH Authentication/Authroization system migration to AWS – helped in AWS resource configuration, troubleshooting and cut over.}
        \end{cvitems}
      }

%------------------------------------------------

  \cventry
      {Senior Software Engineer} % Job title
      {Singapore Press Holdings Limited} % Organization
      {Singapore} % Location
      {May. 2015 - Jan. 2019} % Date(s)
      { % Description(s) of tasks/responsibilities
        \begin{cvitems}
          \item {Registration \& Authentication module using OpenAm as IDP. Bug fixes, refactoring and code cleanup, build and deployment automation using Ansible, Migrate from svn to git and standardize gitflow workflow.}
          \item {OpenAm Policy Agent configuration management and migration.}
          \item {YAH, a project built to send out personalized newsletter for each subscriber every day at a specific time. Developed using Vert.x 3.0 \& RxJava in an asynchronous event-based manner as Microservices.}
          \item {Built and Maintained Consent Tracking System to track the consents submitted and updated by online public users. In particular system will be tracking user’s consent to receive, SPH promotional/marketing materials and third party promotional/marketing materials. - Java, Vert.x 2.0, MongoDB}
          \item {OpenDJ user accounts housekeep and merge legacy accounts - Scala, Hadoop, Spark, OpenDJ, Shell scripts }
          \item {Penetration testing on OpenAm IDP and Registration Authentication module. Performed testing on Kali linux using w3af, zaproxy for OWASP top 10 vulnerabilities. Analyzing network vulnerability using nmap, sslscan.  Resolving reflected xss, unvalidated redirects and forwards, information leakage and SSL cipher suites tightening.}
          \item {Setup Spark standalone cluster with R support, setup using own docker images. Created the first alpine R image and submitted APKBUILD to testing alpine pkg repo.}
        \end{cvitems}
      }

%------------------------------------------------

  \cventry
      {Software Engineer} % Job title
      {hSenid Mobile Solutions Pvt Ltd.} % Organization
      {Sri Lanka} % Location
      {Apr. 2014 - Mar. 2015} % Date(s)
      { % Description(s) of tasks/responsibilities
        \begin{cvitems}
          \item {Research about GPRS core network elements such as GGSN and HLR. Developed a basic simulator for HLR.}
          \item {Research on M2M and IOT. M2M ETSI architecture, M2M service capabilities, bootstrapping \& security and existing challenges.}
          \item {Worked in bug fixes for SMSC (Short Message Service Center) and SMPP (Short Message Peer-to-Peer) Gateway.}
          \item {Signaling optimization in SIGTRAN gateway - SCCP Routing Control, SCCP Management Messages, SCTP – Multihoming}
          \item {Adding change requirements to the SMPP provisioning UI - an interface to create SMSC, SMPP-GW connections, routing rules and ESME.}
        \end{cvitems}
      }

%------------------------------------------------

  \cventry
      {Industrial Trainee} % Job title
      {Lanka Communication Services (PVT) Ltd.} % Organization
      {Sri Lanka} % Location
      {May. 2012 - Dec. 2012} % Date(s)
      { % Description(s) of tasks/responsibilities
        \begin{cvitems}
          \item {IP Management System for network planning team of LankaCom using PHP and MySQL with CodeIgniter framework.}
        \end{cvitems}
      }

%------------------------------------------------

\end{cventries}